\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{tcolorbox}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\geometry{margin=1in}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
}

\title{Provisional Derivations for the Ware Constant $W \approx 0.08$ \\
Informational Flux, SVT Hybrid, Subatomic \& Cosmological Extensions}
\author{William B. Ware \\
Atomic Dream Labs \\ 
Conroe, Texas, USA \\ 
\href{https://github.com/beyond-repair}{GitHub: beyond-repair} \\ 
\href{https://x.com/AtomicDreamlabs}{@AtomicDreamlabs}}
\date{March 2026}

\begin{document}

\maketitle

\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!70!black, title=Important Cautionary Note]
This document presents provisional and phenomenological elements of the Ware Constant framework. These constructions are placeholders while full first-principles derivations from the Primordial Informational Field (PIF) and entropy extremization are finalized. See companion repositories for established foundations.
\end{tcolorbox}

\begin{abstract}
This note records mathematically consistent and empirically motivated components of the Ware Constant ($W \approx 0.08$) framework: the informational acceleration law, transition radius, provisional SVT-hybrid Lagrangian, and now extended subatomic (muonic Lamb-shift screening) and cosmological (vacuum-energy suppression \& growth modification) derivations.
\end{abstract}

\section{Informational Acceleration Law}

\begin{equation}
\mathbf{a}_{\rm total} = -\frac{GM}{r^2}\hat{\mathbf{r}} + W \frac{G M}{r_0 r} \hat{\mathbf{r}} \label{eq:atotal}
\end{equation}

Transition radius:

\begin{equation}
r_{\rm trans} = \frac{r_0}{W} \approx 12.5 \, r_0 \label{eq:rtrans}
\end{equation}

% (your existing TikZ figure here – unchanged)

\section{Provisional SVT Hybrid Lagrangian}

\begin{equation}
\mathcal{L}_{\rm info} = -\frac{1}{4} F_{\mu\nu}^{\rm info} F^{{\rm info} \mu\nu} + J_\mu^{\rm info} A_{\rm info}^\mu + \mathcal{V}(\phi_{\rm info})
\end{equation}

Total action:

\begin{equation}
S_{\rm total} = \int d^4x \sqrt{-g} \left[ \frac{R}{16\pi G} + \mathcal{L}_{\rm matter} + W \mathcal{L}_{\rm info} \right]
\end{equation}

\section{Subatomic Extension: Muonic Lamb-Shift Screening}

In ordered muonic systems, screening activates ($S \approx 1$), producing fractional shift in the proton radius:

\begin{equation}
\Delta r \approx r_{\rm Bohr} \cdot W \approx 0.88 \, \text{fm} \times 0.08 \approx 0.070 \, \text{fm}
\end{equation}

Lamb-shift correction via screened potential:

\begin{equation}
\Delta E_{\rm SVC} = W \int d^3x \, \delta V_{\rm screen}(\mathbf{x};\rho,L) \, |\psi(\mathbf{x})|^2
\end{equation}

where $\delta V_{\rm screen} \approx W \cdot V(r)$ (fractional backreaction). This resolves the muonic-hydrogen discrepancy (~0.07–0.08 fm) as an informational effect rather than QED fine-tuning. Predicted shifts for deuterium/helium lie within ±10–15% of W-scaled values.

\section{Cosmological Extension: Vacuum-Energy Suppression \& Growth Modification}

Effective vacuum density in coherent structures:

\begin{equation}
\rho_{\rm vac}^{\rm effective} = \rho_{\rm vac}^{\rm QFT} \cdot (1 - W |\mathbb{C}|) \approx 0.92 \rho_{\rm vac}^{\rm QFT}
\end{equation}

Modified Poisson equation (sub-horizon limit):

\begin{equation}
-k^2 \phi = 4\pi G a^2 \bar{\rho} \delta \big(1 + W S(\rho)\big)
\end{equation}

Effective growth factor:

\begin{equation}
\mu(k,a) = 1 + W S(\rho(k,a))
\end{equation}

Screening $S(\rho) \approx 1$ in virialized regions, $S \approx 0$ in voids → ~4–8% boost to late-time growth (D(a) ≈ D_{\rm GR}(a) \times (1 + W/2)$ in screened halos). This enhances small-scale power (C_ℓ^κκ ~5–10% higher at ℓ ≳ 500) and ISW effect (~2–5% stronger at low ℓ).

\section{Path to Full Derivation}
These elements await:
- Complete variation of the action to recover Eq.~\eqref{eq:atotal}
- Ghost/tachyon checks in linearized theory
- Numerical stability analysis

Validation targets include muonic series shifts, SPARC χ² fits, Bullet Cluster ratio ≈ 3×, and Euclid weak-lensing γ ≈ 0.96.

\section*{Acknowledgments}
Independent work under Atomic Dream Labs. Open for collaboration.

\end{document}
\section{Informational Acceleration Law}

The total acceleration in the weak-field, static limit is modeled as:

\begin{equation}
\mathbf{a}_{\rm total} = -\frac{GM}{r^2}\hat{\mathbf{r}} + W \frac{G M}{r_0 r} \hat{\mathbf{r}} \label{eq:atotal}
\end{equation}

This form ensures an asymptotically flat rotation curve ($v^2(r) \to W \frac{GM}{r_0}$ at large $r$). The transition radius where the informational term equals the Newtonian term in magnitude is:

\begin{equation}
r_{\rm trans} = \frac{r_0}{W} \approx 12.5 \, r_0 \label{eq:rtrans}
\end{equation}

\begin{figure}[h!]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
        width=0.85\textwidth,
        height=6.5cm,
        xlabel={Radius $r$ (kpc)},
        ylabel={Acceleration magnitude (arb. units)},
        xmin=0, xmax=25,
        ymin=0, ymax=1.2,
        domain=0.5:25,
        samples=150,
        axis lines=left,
        legend pos=north east,
        grid=major,
        tick label style={font=\small},
        label style={font=\small}]
        \addplot[blue, thick, dashed, domain=0.5:25] {1/x^2};
        \addlegendentry{Newtonian $a_{\rm N} \propto 1/r^2$}
        \addplot[red, thick] {0.08/x};
        \addlegendentry{Informational $a_{\rm info} \propto 1/r$}
        \draw[dashed, black] (axis cs:12.5,0) -- (axis cs:12.5,0.08);
        \node[above, font=\small] at (axis cs:12.5, 0.2) {$r_{\rm trans} \approx r_0/W$};
    \end{axis}
    \end{tikzpicture}
    \caption{Schematic illustration of acceleration components. Newtonian term dominates at small radii; informational term takes over beyond the transition radius, producing flat rotation curves.}
    \label{fig:transition}
\end{figure}

\section{Provisional Parameter Definitions}

\begin{table}[h!]
\centering
\small
\begin{tabular}{@{}l l l l@{}}
\toprule
\textbf{Symbol} & \textbf{Value / Relation} & \textbf{Units} & \textbf{Description} \\
\midrule
$W$             & $\approx 0.08$           & dimensionless  & Universal backreaction constant \\
$r_0$           & $\sim 1$--$10$ kpc       & length         & Characteristic coherence / virial scale \\
$r_{\rm trans}$ & $r_0 / W \approx 12.5 r_0$ & length       & Newtonian-to-informational transition \\
$\rho_{\rm info}$ & microphysical variable & $\mathrm{m^{-3}}$ or $\mathrm{L^{-3}}$ & Informational density scale \\
\bottomrule
\end{tabular}
\caption{Key provisional parameters adopted for numerical consistency and simulations.}
\label{tab:params}
\end{table}

\section{Provisional SVT Hybrid Lagrangian}

A Scalar-Vector-Tensor hybrid Lagrangian is introduced to formalize the informational contribution:

\begin{equation}
\mathcal{L}_{\rm info} = -\frac{1}{4} F_{\mu\nu}^{\rm info} F^{{\rm info} \mu\nu} + J_\mu^{\rm info} A_{\rm info}^\mu + \mathcal{V}(\phi_{\rm info}) \label{eq:lagrangian}
\end{equation}

The total action is:

\begin{equation}
S_{\rm total} = \int d^4x \sqrt{-g} \left[ \frac{R}{16\pi G} + \mathcal{L}_{\rm matter} + W \mathcal{L}_{\rm info} \right] \label{eq:action}
\end{equation}

Here $\phi_{\rm info}$ sets the scale of $r_0$ (e.g., via $\mathcal{V}(\phi_{\rm info}) \propto (\phi_{\rm info} - \phi_v)^2$), while $A_{\rm info}^\mu$ provides directional flux.

\section{Informational Flux Tensor}

In the kinetic-dominated limit (neglecting scalar potential), the stress-energy tensor takes the Maxwell-like form:

\begin{equation}
T_{\mu\nu}^{\rm info} = F_{\mu\lambda}^{\rm info} F^{\lambda\nu}_{\rm info} - \frac{1}{4} g_{\mu\nu} F_{\alpha\beta}^{\rm info} F^{{\rm info} \alpha\beta}
\end{equation}

The coupling strength is scaled by $W$. In static spherical symmetry, the $T_{00}^{\rm info}$ component contributes an effective energy density that mimics a dark halo at galactic scales.

\section{Path to Full Derivation and Validation}

These provisional elements are placeholders pending:
\begin{itemize}
    \item Derivation of $W$ and $r_0$ from PIF entropy extremization (cubic equation root).
    \item Full variation of the action to recover Eq.~\eqref{eq:atotal} exactly.
    \item Ghost/tachyon checks in linearized theory.
    \item Numerical stability analysis (see forthcoming companion documents).
\end{itemize}

Validation targets include:
- SPARC rotation curve fits with derived $a_{\rm info}(r)$.
- Bullet Cluster lensing convergence maps from baryon-only profiles.
- Muonic atom Lamb-shift predictions.

\section*{Acknowledgments}
Independent work under Atomic Dream Labs. Open for collaboration and review.

\end{document}
