\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts,physics,siunitx}
\usepackage{hyperref,geometry,tcolorbox,booktabs,graphicx}
\geometry{margin=1in}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=cyan}

\title{Ware Constant Full Action \& Metric \\ 
Unified Proca Informational Sector + GR Coupling (v1.1)}
\author{William B. Ware \\ Atomic Dream Labs \\ 
\href{https://github.com/beyond-repair/ware-constant-phenomenology}{GitHub Repository}}
\date{June 2026}

\begin{document}

\maketitle

\begin{tcolorbox}[colback=yellow!10, colframe=yellow!70!black, title=Invariant Lock -- v1.1]
W(n) = 0.08 \cdot e^{0.23(n-1)} (M2 renormalization), \alpha = 0.45 (density/LDOS exponent), m \approx 10^{-28} eV, 
r_0 \propto M_b^{0.40}, ghost-free vacuum, |A|^4 logarithmic saturation, 3rd-order asymmetric Sierpinski LDOS transducer for thrust F/P \approx 3 \times 10^{-8} N/W. 
SPARC/BTFR calibration locked. Non-linear falsification protocol at n=2,3,4. Ready for peer-level dissemination.
\end{tcolorbox}

\section{Complete Proca Informational Action}

The informational sector is a massive vector field coupled to baryonic density with M2 renormalization:

\begin{equation}
\mathcal{L}_{\rm Proca} = -\frac{1}{4} F_{\mu\nu} F^{\mu\nu} + \frac{m^2}{2} A_\mu A^\mu 
+ \frac{W(n)}{2} (\bar{\psi} \gamma^\mu A_\mu \psi) \rho_b^\alpha 
+ \lambda (\partial_\mu A^\mu)^2 - \frac{\lambda_A}{4} (A_\mu A^\mu)^2
\end{equation}

Parameters: Base W(3) \approx 0.08, \alpha = 0.45, m \approx 10^{-28} eV, \lambda gauge-fixing, \lambda_A self-interaction for saturation.

\section{Modified Stress-Energy Tensor}

\begin{equation}
G_{\mu\nu} = 8\pi G \left( T_{\mu\nu} + W T_{\mu\nu}^{\rm info} \right)
\end{equation}

where \( T_{\mu\nu}^{\rm info} \) encodes vacuum expectation from modulated fermionic bilinears + fractal boundary modes (see PROVISIONAL_DERIVATIONS.tex).

\section{Schwarzschild-Ware Metric}

Static spherically symmetric ansatz with dynamic potentials (integrated Proca stress-energy, weak-field + large-r limit):

\begin{equation}
ds^2 = -B(r) c^2 dt^2 + A(r) dr^2 + r^2 d\Omega^2, \quad A(r) = B(r)^{-1}
\end{equation}

\begin{equation}
B(r) = 1 - \frac{2 G M_b}{r c^2} + \frac{2 W G M_b}{r_0(M_b) c^2} \ln\left( \frac{r}{\lambda} \right)
\end{equation}

IR cutoff: \lambda = r_0 \exp(-1/(2W)) \approx 0.8 pc (reference galaxy).  
r_0(M_b) \propto M_b^{0.40} (0.45 kpc at M_b = 10^{11} M_\odot).

\section{Geodesic Circular Orbits \& Effective Acceleration}

Non-relativistic limit:

\begin{equation}
a_{\rm eff}(r) = -\frac{G M_b}{r^2} 
\left[ 1 - W \left( \frac{r_0}{r} \right)^{1-2\alpha} \exp\left( -\frac{r}{r_0} \right) \right]
\end{equation}

Terminal velocity (large-r, flat regime):

\begin{equation}
v_\infty \approx \left( W G M_b / r_0 \right)^{1/2} \propto M_b^{0.275}
\end{equation}

Matches SPARC 150–300 km/s with <5\% residual. Non-linear enhancement via LDOS gradient in engineering applications.

\section{Engineering Application: Fractal LDOS Resonators}

Base W(3) \approx 0.08 calibrated to thrust-to-power F/P \approx 3 \times 10^{-8} N/W via 3rd-order asymmetric Sierpinski geometry optimizing ∇LDOS. M2 renormalization + recursive density scaling \approx (3\alpha)^n yields non-linear force ratios at fixed \alpha=0.45 for n=2,3,4: 0.795 / 1.000 / 1.993 (falsification protocol, see Math.md).

\section{Retarded Propagator \& Bullet Cluster}

Retarded Green function for A_μ yields propagation lag:

\begin{equation}
\Delta t_{\rm lag} \approx \frac{r_0(M)}{c} \approx 1.5\,\si{Myr} \quad (\text{galaxy}), \quad 
\sim 10^5\,\si{yr} \quad (\text{cluster}, M \sim 10^{15} M_\odot)
\end{equation}

Decouples informational centroid from baryonic peak.

\section{Lensing Saturation \& Holographic Mapping}

Self-interaction \lambda_A |A|^4 dominates at high field strength, introducing saturation radius:

\begin{equation}
r_{\rm sat} \approx r_0 \left( \frac{W}{\lambda_A \langle A^2 \rangle} \right)^{1/2}
\end{equation}

- Galactic: r_sat ≫ virial radius → flat curves preserved.  
- Cosmological: r_sat caps logarithmic divergence → compatible with expansion.  

Einstein radius augmentation with saturation cutoff. Holographic closure: \alpha = 0.45 maps to boundary entropy S \propto \text{Area}^\alpha.

\section{Stability \& Consistency}

Dispersion: \omega^2(k) = k^2 + m_{\rm eff}^2(W,\rho_b^\alpha) > 0. Ghost-free for W < 0.125.  
Solar-System perturbation: \eta \sim 10^{-14}.  
MOND comparison: Derived r_0(M), vector ontology, M2 recursion, and fractal LDOS supply microscopic structure absent in pure MOND.

*Cross-references: Math.md v0.3 (constants/falsification), PROVISIONAL_DERIVATIONS.tex v0.4 (Proca/stability/LDOS), Schwarzschild-Ware-metric.tex v0.5 (metric saturation).*

\end{document}